### 2015-02-26 Experimenten/FeatureSet/Grafieken.tex
Grafieken

\documentclass{minimal}

\usepackage{pgfplots}
\pgfplotsset{compat=newest}

@@

Vraag: hoeveel features zijn nodig om een redelijke accuraatheit (=90\% van de grootste accuraatheid) te behalen?

@@

\begin{tikzpicture}
  \begin{axis}[
		xlabel=Aantal features,
		ylabel=Accuraatheid (\%)]
    \addplot +[no markers, raw gnuplot] gnuplot {
        plot "AllFeatures/InfoGain/RandomForest/results.dat" smooth sbezier;
    };
  \end{axis}
\end{tikzpicture}

\begin{tikzpicture}
  \begin{axis}[
		xlabel=Aantal features,
		ylabel=Accuraatheid (\%)]
    \addplot +[no markers, raw gnuplot] gnuplot {
        plot "Statistic/InfoGain/RandomForest/results.dat" smooth sbezier;
    };
  \end{axis}
\end{tikzpicture}

\begin{tikzpicture}
  \begin{axis}[
		xlabel=Aantal features,
		ylabel=Accuraatheid (\%)]
    \addplot +[no markers, raw gnuplot] gnuplot {
        plot "FFT/InfoGain/RandomForest/results.dat" smooth sbezier;
    };
  \end{axis}
\end{tikzpicture}

\begin{tikzpicture}
  \begin{axis}[
		xlabel=Aantal features,
		ylabel=Accuraatheid (\%)]
    \addplot +[no markers, raw gnuplot] gnuplot {
        plot "DWT/InfoGain/RandomForest/results.dat" smooth sbezier;
    };
  \end{axis}
\end{tikzpicture}

\begin{tikzpicture}
  \begin{axis}[
		xlabel=Aantal features,
		ylabel=Accuraatheid (\%)]
    \addplot +[no markers, raw gnuplot] gnuplot {
        plot "HMM/InfoGain/RandomForest/results.dat" smooth sbezier;
    };
  \end{axis}
\end{tikzpicture}

>>>>

\documentclass[tightpage]{standalone}

\usepackage{pgfplots}
\pgfplotsset{compat=newest}
\usepackage{verbatim}
\usepackage{helvet}
\usepackage[eulergreek]{sansmath}
\usepackage{varwidth}

@@

%Vraag: hoeveel features zijn nodig om een redelijke accuraatheit (=90\% van de grootste accuraatheid) te behalen?

@@

\begin{tikzpicture}
  \begin{axis}[
  		title=AllFeatures/InfoGain/RandomForest,
		xlabel=Aantal features,
		ylabel=Accuraatheid (\%),
		width=37cm,
		height=30cm,
		font=\sffamily\sansmath\Huge, % font = Arial, huge=20pt, Huge=24pt
		xtick={0,10,...,140},
		ytick={50,60,...,100}] 
    \addplot +[no markers, raw gnuplot, color=orange, line width=2mm] gnuplot {
        plot "AllFeatures/InfoGain/RandomForest/results.dat" smooth sbezier;
    };
  \end{axis}
\end{tikzpicture}

\begin{tikzpicture}
  \begin{axis}[
  		title=Statistic/InfoGain/RandomForest,
		xlabel=Aantal features,
		ylabel=Accuraatheid (\%),
		width=37cm,
		height=30cm,
		font=\sffamily\sansmath\Huge, % font = Arial, huge=20pt, Huge=24pt
		xtick={0,4,...,20},
		ytick={50,60,...,100}] 
    \addplot +[no markers, raw gnuplot, color=orange, line width=2mm] gnuplot {
        plot "Statistic/InfoGain/RandomForest/results.dat" smooth sbezier;
    };
  \end{axis}
\end{tikzpicture}

\begin{tikzpicture}
  \begin{axis}[
  		title=DWT/InfoGain/RandomForest,
		xlabel=Aantal features,
		ylabel=Accuraatheid (\%),
		width=37cm,
		height=30cm,
		font=\sffamily\sansmath\Huge, % font = Arial, huge=20pt, Huge=24pt
		xtick={0,6,...,30},
		ytick={50,60,...,100}] 
    \addplot +[no markers, raw gnuplot, color=orange, line width=2mm] gnuplot {
        plot "DWT/InfoGain/RandomForest/results.dat" smooth sbezier;
    };
  \end{axis}
\end{tikzpicture}

\begin{tikzpicture}
  \begin{axis}[
  		title=FFT/InfoGain/RandomForest,
		xlabel=Aantal features,
		ylabel=Accuraatheid (\%),
		width=37cm,
		height=30cm,
		font=\sffamily\sansmath\Huge, % font = Arial, huge=20pt, Huge=24pt
		xtick={0,10,...,84},
		ytick={50,60,...,100}] 
    \addplot +[no markers, raw gnuplot, color=orange, line width=2mm] gnuplot {
        plot "FFT/InfoGain/RandomForest/results.dat" smooth sbezier;
    };
  \end{axis}
\end{tikzpicture}

\begin{tikzpicture}
  \begin{axis}[
  		title=HMM/InfoGain/RandomForest,
		xlabel=Aantal features,
		ylabel=Accuraatheid (\%),
		width=37cm,
		height=30cm,
		font=\sffamily\sansmath\Huge, % font = Arial, huge=20pt, Huge=24pt
		xtick={0,2,...,10},
		ytick={50,60,...,100}] 
    \addplot +[no markers, raw gnuplot, color=orange, line width=2mm] gnuplot {
        plot "HMM/InfoGain/RandomForest/results.dat" smooth sbezier;
    };
  \end{axis}
\end{tikzpicture}
